Certified Desugaring of Javascript Programs using Coq

### 2016-12-15 paper/paper.tex
Simpler correctness/completeness.

\begin{minted}{coq}
Inductive resultof (T : Type) : Type :=
| result_some : T -> resultof T
| result_fail : string -> resultof T        (* program error *)
| result_impossible : string -> resultof T  (* inconsistency *)
| result_bottom : resultof T                (* out of fuel *)
| result_dump : ctx -> store -> resultof T  (* dump state *)

Definition eval runs c st (e : expr) : result :=
  let return_value := result_value st in
  match e with
  | expr_empty => return_value value_empty
  | expr_undefined => return_value value_undefined
...

Record runs_type : Type := runs_type_intro {
    runs_type_eval : ctx -> store -> expr -> result
}.

Definition runs_0 := {|
    runs_type_eval := fun c st _ => result_bottom
  |}
.

Definition runs_S runs := 
  let wrap {A : Type} (f : runs_type -> ctx -> store -> A) c st : A :=
    f runs c st
  in {|
    runs_type_eval := wrap eval
  |}
.

Fixpoint runs max_step : runs_type :=
  match max_step with
  | 0 => runs_0
  | S max_step' => runs_S (runs max_step')
  end
.

Lemma eval_complete : forall c st e o,
  red_expr c st e o -> 
  exists k, runs_type_eval (runs k) c st e = result_some o.

Record runs_type_correct runs :=
    make_runs_type_correct {
        runs_type_correct_eval : forall c st e o,
            runs_type_eval runs c st e = result_some o -> red_expr c st e o
}.

Lemma eval_correct : forall runs c st e o,
  runs_type_correct runs -> 
  eval runs c st e = result_some o ->
  red_expr c st e o.

Lemma runs_correct : forall k, runs_type_correct (runs k). 
\end{minted}

>>>>

\begin{minted}{coq}
Inductive resultof (T : Type) : Type :=
| result_some : T -> resultof T
| result_fail : string -> resultof T        (* program error *)
| result_impossible : string -> resultof T  (* inconsistency *)
| result_bottom : resultof T                (* out of fuel *)
| result_dump : ctx -> store -> resultof T. (* dump state *)

Definition eval_S eval c st (e : expr) : result :=
  let return_value := result_value st in
  match e with
  | expr_empty => return_value value_empty
  | expr_undefined => return_value value_undefined
...

Definition eval_0 : eval_fun := fun c st _ => result_bottom.

Fixpoint eval_k max_step : eval_fun :=
  match max_step with
  | 0 => eval_0
  | S max_step' => eval_S (eval_k max_step')
  end
.

Lemma eval_k_complete : forall c st e o,
  red_expr c st e o -> 
  exists k, eval_k k c st e = result_some o.

Record eval_fun_correct eval := forall c st e o,
  eval c st e = result_some o -> red_expr c st e o.

Lemma eval_k_correct : forall k, runs_type_correct (eval k). 
\end{minted}
